Improved Smooth Free-Form Deformation with Sharp Feature Awareness

### 2016-08-15 paper.tex
save fighting!!!!!

\section{OpenGL compute shader}
CUDA which is used for implement Smooth FFD is a parallel computing platform and programming model invented by NVIDIA. It enables dramatic increases in computing performance by harnessing the power of the graphics processing unit (GPU). Nevertheless, only on the Nvidia GPU can CUDA run. It lead to the compatibility problems in other desktop gpu as well as mobile platform which is rapid developing in recent years.

While Compute Shader is a OpenGL Shader Stage that is used entirely for computing arbitrary information. It is available in every platform as long as it is surpport OpenGL 4.3.

@@

\begin{figure}[htbp]
\begin{center}
	\begin{minipage}[l]{0.54\textwidth}
		\centering
		\subfloat[]{\includegraphics[width=0.24\linewidth]{pic/ship_ori.png}}
		\subfloat[]{\includegraphics[width=0.24\linewidth]{pic/ship_cym.png}}
		\subfloat[]{\includegraphics[width=0.24\linewidth]{pic/ship_ac.png}}
		\subfloat[]{\includegraphics[width=0.24\linewidth]{pic/ship_ac_tex.png}}
		\caption{Deformation of the Ship model by a $3\times3\times3$ B-spline volume with $5\times8\times5$ control points}
		\label{fig:ship}
	\end{minipage}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
	\begin{minipage}[c]{0.63\textwidth}
		\centering
		\subfloat[]{\includegraphics[width=0.242\linewidth]{pic/rabbit_ori.png}}
		\subfloat[]{\includegraphics[width=0.242\linewidth]{pic/rabbit_cym.png}}
		\subfloat[]{\includegraphics[width=0.242\linewidth]{pic/rabbit_ac.png}}
		\subfloat[]{\includegraphics[width=0.242\linewidth]{pic/rabbit_ac_tex.png}}
		\caption{Deformation of the Rabbit model by a $2\times2\times2$ B-spline volume with $5\times8\times5$ control points}
		\label{fig:rabbit}
	\end{minipage}
\end{center}
\end{figure}

@@

The efficiencies obtained with improve smooth FFD and \cite{Cui15} are compared in Table \ref{tab:compare_pre} and Table \ref{tab:compare_deform}. The model we use is shown in Figure~\ref{fig:snail}; this model has 46,742 faces. As in Section \ref{sec:comparison_of_rendering}, each triangular B\'ezier patch is tessellated into 100 sub-triangles. The degree of the B-spline volume is $2\times2\times2$, with $5\times5\times5$ control points. Table\ref{tab:compare_pre} illustrates that the speed of our method is faster than that of \cite{Cui15} due to clip triangle by GPU which \cite{Cui15} do it by CPU. In the deformation stage, the two method have almost the same efficiencies. The proposed method is sufficiently fast to handle large models in real time.

\begin{figure}
  \centering
  \subfloat[][]{\includegraphics[width=.45\textwidth]{pic/snail1}}\hfill
  \subfloat[][]{\includegraphics[width=.45\textwidth]{pic/snail2}}\hfill
  \caption{Relationship of l and sub-triangles number}
  \label{fig:snail}
\end{figure}

\begin{minipage}[c]{0.7\textwidth} 
  \centering
  \footnotesize
    \tabcaption{Comparison of the efficiencies of our method and \cite{Cui15}(pre-compute stage)}
  \begin{tabular}{llll}
  	\hline
  	Step & Our method & \cite{Cui15}\\
  	\hline
  	Generate PN-triangle         & 4.618   & 104.465     \\
  	Clip triangle                & 21.475  & 5027.418    \\
  	\hline
  	total                        & 26.093  & 5131.883    \\
  	\hline
  \end{tabular}
    \label{tab:compare_pre}
\end{minipage}

\begin{minipage}[c]{0.7\textwidth} 
  \centering
  \footnotesize
    \tabcaption{Comparison of the efficiencies of our method and \cite{Cui15}(deform stage)}
  \begin{tabular}{llll}
  	\hline
  	Step & Our method & \cite{Cui15}\\
      %%\hline
      %%Copy control points to the GPU    & 0.004   & 0.287     \\
  	\hline
      Calculate the sampling points     & \multirow{6}{*}{67.419} & 30.522     \\
  	Calculate the constraint points   &   & 10.874     \\
  	Calculate the control points      &   & 11.125     \\
  	Calculate the adjusting normals   &   & 4.209     \\
  	Adjust the control points         &   & 4.344     \\
  	Calculate the tessellation points &   & 4.057     \\
  	\hline
  	total                             & 67.419  & 65.464    \\
  	\hline
  \end{tabular}
  \label{tab:compare_deform}
\end{minipage}

\subsection{Approximation error tests}
In the smooth FFD, both the geometry and normal are obtained approximately via constrained fitting. Thus, there
are approximation errors in the geometry and normal compared with the accurate FFD. Since the smooth parts of a
polygonal object can be regarded as a piecewise linear approximation of a potentially smooth shape, which is unknown in
general, thus it is difficult to evaluate the approximation errors.

>>>>

\section{OpenGL compute shader}
CUDA which is used for implement Smooth FFD is a parallel computing platform and programming model invented by NVIDIA. It enables dramatic increases in computing performance by harnessing the power of the graphics processing unit (GPU). Nevertheless, only on the NVIDIA GPU can CUDA runs. It lead to the compatibility problems in other desktop GPU as well as mobile platform which is rapid developing in recent years.

While Compute Shader is an OpenGL Shader Stage that is used entirely for computing arbitrary information. It is available in every platform as long as it supports OpenGL 4.3.

@@

\begin{figure}[htbp]
\begin{center}
	\begin{minipage}[l]{0.99\textwidth}
		\centering
		\subfloat[]{\includegraphics[width=0.24\linewidth]{pic/ship_ori.png}}
		\subfloat[]{\includegraphics[width=0.24\linewidth]{pic/ship_cym.png}}
		\subfloat[]{\includegraphics[width=0.24\linewidth]{pic/ship_ac.png}}
		\subfloat[]{\includegraphics[width=0.24\linewidth]{pic/ship_ac_tex.png}}
		\caption{Deformation of the Ship model by a $3\times3\times3$ B-spline volume with $5\times8\times5$ control points}
		\label{fig:ship}
	\end{minipage}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
	\begin{minipage}[c]{0.99\textwidth}
		\centering
		\subfloat[]{\includegraphics[width=0.242\linewidth]{pic/rabbit_ori.png}}
		\subfloat[]{\includegraphics[width=0.242\linewidth]{pic/rabbit_cym.png}}
		\subfloat[]{\includegraphics[width=0.242\linewidth]{pic/rabbit_ac.png}}
		\subfloat[]{\includegraphics[width=0.242\linewidth]{pic/rabbit_ac_tex.png}}
		\caption{Deformation of the Rabbit model by a $2\times2\times2$ B-spline volume with $5\times8\times5$ control points}
		\label{fig:rabbit}
	\end{minipage}
\end{center}
\end{figure}

@@

The efficiencies obtained with improve smooth FFD and \cite{Cui15} are compared in Table \ref{tab:compare_pre} and Table \ref{tab:compare_deform}. The model we use is shown in Figure \ref{fig:snail}. This model has 46,742 faces. As in Section \ref{sec:comparison_of_rendering}, each triangular B\'ezier patch is tessellated into 100 sub-triangles. The degree of the B-spline volume is $2\times2\times2$, with $5\times5\times5$ control points. Table\ref{tab:compare_pre} illustrates that the speed of our method is faster than that of \cite{Cui15} due to clip triangle by GPU which \cite{Cui15} do it by CPU. In the deformation stage, the total time of all stages of Cui's method is 65.464ms. Our method just has an overall run time, 67.419ms, because we implement all of the stages in the same shader while there's not a suitable method to measure time inside a shader. the two method have almost the same efficiencies. The proposed method is sufficiently fast to handle large models in real time.

\begin{figure}
  \centering
  \subfloat[][rendering result of Cui et al.\cite{Cui15}]{\includegraphics[width=.45\textwidth]{pic/snail1}}\hfill
  \subfloat[][rendering result of our mothod]{\includegraphics[width=.45\textwidth]{pic/snail2}}\hfill
  \caption{Model used by comparison of efficiencies}
  \label{fig:snail}
\end{figure}

\begin{minipage}[c]{0.99\textwidth} 
  \centering
  \footnotesize
    \tabcaption{Comparison of the efficiencies of our method and \cite{Cui15}(pre-compute stage)}
  \begin{tabular}{llll}
  	\hline
  	Step & Our method & \cite{Cui15}\\
  	\hline
  	Generate PN-triangle         & 4.618   & 104.465     \\
  	Clip triangle                & 21.475  & 5027.418    \\
  	\hline
  	total                        & 26.093  & 5131.883    \\
  	\hline
  \end{tabular}
    \label{tab:compare_pre}
\end{minipage}

\begin{minipage}[c]{0.99\textwidth} 
  \centering
  \footnotesize
    \tabcaption{Comparison of the efficiencies of our method and \cite{Cui15}(deform stage)}
  \begin{tabular}{llll}
  	\hline
  	Step & Our method & \cite{Cui15}\\
      %%\hline
      %%Copy control points to the GPU    & 0.004   & 0.287     \\
  	\hline
      Calculate the sampling points     & \multirow{6}{*}{67.419} & 30.522     \\
  	Calculate the constraint points   &   & 10.874     \\
  	Calculate the control points      &   & 11.125     \\
  	Calculate the adjusting normals   &   & 4.209     \\
  	Adjust the control points         &   & 4.344     \\
  	Calculate the tessellation points &   & 4.057     \\
  	\hline
  	total                             & 67.419  & 65.464    \\
  	\hline
  \end{tabular}
  \label{tab:compare_deform}
\end{minipage}

\subsection{Approximation error tests}
not finish!!!!!!!!!!!!!!!!!!!!

In the smooth FFD, both the geometry and normal are obtained approximately via constrained fitting. Thus, there
are approximation errors in the geometry and normal compared with the accurate FFD. Since the smooth parts of a
polygonal object can be regarded as a piecewise linear approximation of a potentially smooth shape, which is unknown in
general, thus it is difficult to evaluate the approximation errors.
